Timeliness of security updates for Android

### 2015-03-20 securityupdates.tex
Drop a couple of figures

\begin{figure}[h]
 \includegraphics[width=\columnwidth]{figures/nw_security_updates.pdf}
 \caption{Proportion of updates each week which (may have) fixed vulnerabilities}
 \label{fig:weekly_security_updates}
\end{figure}
We recorded update events and Figure~\ref{fig:from_to_updates} shows how devices upgrade between different versions of Android.
Mostly the dark cells are upgrades (above the diagonal) (\daNumUpdatesUpgrades).
While many upgrades are from one version to the next version there are also a fair number (\daNumUpdatesBigUpgrades, \daPercBigUpgradesNominal) which skip more than \daNumUpdatesSkippedBig\ versions.
Surprisingly there are also a small number of downgrade events (\daNumUpdatesDowngrades, \daPercUpdatesDowngradesNominal) when older versions of Android are installed on to devices.
Possible reasons why users are downgrading are to free up space on their device, to make it easier to root or because a new version introduced bugs.

@@

\section{Threats to validity}
\label{sec:validity}
\subsection{The \da\ data gives a conservative estimate of the Android version distribution}
\label{sec:representative}
\begin{figure}
 \centering
 \begin{subfigure}[b]{\columnwidth}
 \includegraphics[width=\columnwidth]{figures/googleplayapi}
 \caption{Google Play data on proportion of devices running different API versions}
 \label{fig:play_api}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
 \includegraphics[width=\columnwidth]{figures/norm_api_gpcomp}
 \caption{\da\ data on proportion of devices running different API versions}
 \label{fig:da_api}
\end{subfigure}
\caption{Monthly Android API version data}
\end{figure}
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/api_gpcomp_rdiff}
 \caption{Difference between \da\ and Google Play data on the proportion of devices running different Android API versions}
 \label{fig:da_gp_comp_diff}
\end{figure}
The data from \da\ we used to investigate the proportion of devices exposed to different vulnerabilities is the OS version.
Unfortunately there is no ground truth of OS version information.
However Google has published API version information almost every month since December 2009 and we have collated this information.\footnote{\url{http://androidvulnerabilities.org/play/historicplaydashboard}}
While API versions are too coarse grained to use for security update detection they are closely related to OS versions and so if the \da\ data on API versions are similar to the Google data on API versions then the \da\ data on OS versions should be representative.
Figure~\ref{fig:play_api} shows the data from Google and Figure~\ref{fig:da_api} shows the data from \da\ and they appear similar.
Figure~\ref{fig:da_gp_comp_diff} shows the difference between Figures~\ref{fig:play_api} and \ref{fig:da_api}, normalising for days since the API version was released.
It shows that the \da\ data systematically overestimates the prevalence of new API versions and underestimates the prevalence of old API versions.
This means that the OS version information from \da\ is likely to be overestimating the prevalence of new OS versions and hence our results are a conservative estimate of the security of Android.
This allows us to have confidence in the OS version information.
\todolater{we want a statistical metric to claim this strongly with.}

>>>>

We recorded \daNumFullVersionUpdates\ update events and found most are upgrades (\daNumUpdatesUpgrades).
While many upgrades are from one version to the next version there are also a fair number (\daNumUpdatesBigUpgrades, \daPercBigUpgradesNominal) which skip more than \daNumUpdatesSkippedBig\ versions.
Surprisingly there are also a small number of downgrade events (\daNumUpdatesDowngrades, \daPercUpdatesDowngradesNominal) when older versions of Android are installed on to devices.
Possible reasons why users are downgrading are to free up space on their device, to make it easier to root or because a new version introduced bugs.

@@

\section{Threats to validity}
\label{sec:validity}
\subsection{The \da\ data gives a conservative estimate of the Android version distribution}
\label{sec:representative}
\begin{figure}
 \centering
 \begin{subfigure}[b]{\columnwidth}
 \includegraphics[width=\columnwidth]{figures/googleplayapi}
 \caption{Google Play data on proportion of devices running different API versions}
 \label{fig:play_api}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
 \includegraphics[width=\columnwidth]{figures/norm_api_gpcomp}
 \caption{\da\ data on proportion of devices running different API versions}
 \label{fig:da_api}
\end{subfigure}
\caption{Monthly Android API version data}
\end{figure}

The data from \da\ we used to investigate the proportion of devices exposed to different vulnerabilities is the OS version.
Unfortunately there is no ground truth of OS version information.
However Google has published API version information almost every month since December 2009 and we have collated this information.\footnote{\url{http://androidvulnerabilities.org/play/historicplaydashboard}}
While API versions are too coarse grained to use for security update detection they are closely related to OS versions and so if the \da\ data on API versions are similar to the Google data on API versions then the \da\ data on OS versions should be representative.
Figure~\ref{fig:play_api} shows the data from Google and Figure~\ref{fig:da_api} shows the data from \da\ and they appear similar.
We analysed the difference between the API version data from \da\ and Gooble Play, normalising for days since the API version was released.
This that the \da\ data systematically overestimates the prevalence of new API versions and underestimates the prevalence of old API versions (except for API version 17 which was particularly popular in a focused study discussed in the next section and so was temporarily overestimated when an old version).
This means that the OS version information from \da\ is likely to be overestimating the prevalence of new OS versions and hence our results are a conservative estimate of the security of Android.
This allows us to have confidence in the OS version information.
\todolater{we want a statistical metric to claim this strongly with.}
